An Algorithm for In-Situ Bus Scheduling and Passenger State Update

### 2019-04-19 Report/paper.tex
More prose

\section{Implementation}
This in-situ bus scheduling algorithm was implemented in C\# using the .NET Microframework. It makes use of the Samraksh Emulator to simulate a (potentially large) network of buses and bus stops.

\subsection{.NOW motes vs. Emulator}
This project was implemented on the Samraksh Emulator, not .NOW motes. The reasons for this are varied, but one deciding factor was a lack of availability of motes to use in testing and demonstration. Because this project was built as part of the curriculum for a semester-long class, the developers had access to at most three motes. Unfortunately, any interestin gdemonstration of the algorithm involves at least three bus stops and two buses; that is, five motes would have ben an absolute minimum to showcase the capabilities of this algorithm. Thus, the devision was made to implement the project using the Samraksh Emulator, of which arbitrarily many instances can be launched to simulate an arbitrarily large network. Using the emulator instead of motes also enabled some simplifications to the protocol which made it possible to produce a high-quality project in the time allotted.

@@

Also required was an interface, \lstinline{IMessagePayload}, to be implemented by any component which might need to be included in a message in this system. Such components include \lstinline{Route}, \lstinline{DateTime},\footnote{A payload with type \lstinline|DateTime| is actually a wrapper type, \lstinline|PayloadDateTime| due to C\# restrictions on extending \lstinline|struct|s.} \lstinline{Request}, and others.

\subsection{Testing and Evaluation}
\subsection{Limitations, Challenges, and Omissions}
\subsubsection{Passenger Behavior}
\label{sub:passengers}
Initially, the plan for simulating passengers was to randomly generate requests on the fly, which would be served and assigned by appropriate bus stops. However, the inherent limitations of the .NET Microframework proved insurmountable given the relatively short time frame.

@@

\subsection{Using the Smart-Bus Application}

>>>>

\section{Implementation}
This in-situ bus scheduling algorithm was implemented in C\# using the .NET Microframework. It makes use of the Samraksh Emulator to simulate a (potentially large) network of buses and bus stops, as well as a sequence of passenger requests.

\subsection{.NOW motes vs. Emulator}
This project was implemented on the Samraksh Emulator, not .NOW motes. The reasons for this are varied, but one deciding factor was a lack of availability of motes to use in testing and demonstration. Because this project was built as part of the curriculum for a semester-long class, the developers had access to at most three motes. Unfortunately, an interesting demonstration of the algorithm involves at least three bus stops and one bus. Evaluating the efficacy and scalability of the algorithm with such a limited number of nodes would be impossible. Thus, the decision was made to implement the project using the Samraksh Emulator, of which arbitrarily many instances can be launched to simulate an arbitrarily large network. Using the emulator instead of motes also enabled some simplifications to the protocol which made it possible to produce a high-quality project in the time allotted.

@@

Also required was an interface, \lstinline{IMessagePayload}, to be implemented by any component which might need to be included in a message in this system. Such components include \lstinline{Route}, \lstinline{DateTime},\footnote{A payload with type \lstinline|DateTime| is enclosed by a wrapper type, \lstinline|PayloadDateTime| due to C\# restrictions on extending \lstinline|struct|s.} \lstinline{Request}, and others.

\subsection{Limitations, Challenges, and Omissions}
\subsubsection{Passenger Behavior}
\label{sub:passengers}
Initially, the plan for simulating passengers was to randomly generate requests on the fly, which would be served and assigned by appropriate bus stops. However, the inherent limitations of the .NET Microframework proved insurmountable given the relatively short time frame.

@@

\subsection{Testing and Evaluation}
The efficacy of this (admittedly complicated) distributed algorithm versus a naive, static scheduling approach was evaluated. The static scheduling approach is similar to that employed by real public bus systems in the world: there are $n$ buses, each with a predetermined route $R$ through a number of stops.

Evaluation metrics include
\begin{itemize}
	\item The number of buses required to service $k$ passenger requests on time (lower is better)
	\item The number of requests that can be served on time with $n$ buses (higher is better)
\end{itemize}

\subsubsection{Specification of Static Approach}

\subsubsection{Request Patterns}
A variety of request patterns were used for evaluation. The scales of these patterns range from two passengers to ???, from three bus stops to ???, and from two buses to ???.

\section{Using the Smart-Bus Application}
There are several steps to running the application:
\begin{itemize}
	\item Launch $n$ instances of \lstinline{Bus-Driver}
	\item Launch $m$ instances of \lstinline{Bus-Stop-Driver}
	\item Ensure the simulation parameters of \lstinline{Request-Driver} match the number of buses and stops that have been launched
	\item Launch an instance of \lstinline{Request-Driver} with the requisite simulation parameters (i.e., Request Pattern and Time Multiplier)
	\item Wait for simulation to conclude
\end{itemize}

\subsection{Extending the Smart-Bus Application}
It is, of course, possible to extend or improve the functionality of this application in many ways.
\begin{itemize}
	\item For work on generating dynamic requests, implement the \lstinline{RequestPattern} interface 
	\item To change the request assignment behavior, modify the \lstinline{BusStop} class in \lstinline{Utilities and Classes}
	\item To implement breadth-first search to find buses, modify the \lstinline{BusStopDriver} class
	\begin{itemize}
		\item Changes to \lstinline{Bus} will also be necessary to restrict its responses to those stops within its immediate vicinity
	\end{itemize}
\end{itemize}
